The WISE $W4$ Compendium: I. Introducing the WW4C with $z>4$ Quasars

### 2019-02-15 tex/older_tex/VHzQ_pre2019/WW4C_VHzQ_20180430.tex
big udpate of tex/older_tex/VHzQ_pre2019/ and Lz/

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Very high redshift quasars (VH$z$Qs, defined here to have redshifts
$z\gtrsim5$) are excellent probes of the early Universe. This includes
studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
Volonteri2010, Agarwal2016, Valiante2018, Latif2018} and early metal
enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.

%The build-up of SMBHs via accretion is important due to the desire to understand the evolution of the black hole mass function (BHMF) and since there is a remarkable similarity between cosmic star-formation rate density (SFRD) and black hole accretion rate (BHAR). The SFRD and BHAR trace each other \citep[with a normalisation factor of $\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts $z=0-4$.  However, new results \citet[e.g., ][]{Vito2018a, Calhau2018} suggest that the SFRD and BHAR do not have the same evolutionary form at higher, $z>4$ redshifts, for reasons that are currently poorly understood.  For some high-$z$ QSOs we can measure BHAR and SFR: most have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at $z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g., ][]{Netzer2014}. 
%%However, we also note the potential for the non-causal origins of the
%%black-hole galaxy scaling relations \citep{Jahnke2011}.

@@

\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17
(55\%) of the then known 31 quasars at $z > 6$. However,
\citet{Blain2013} was compiled with the WISE `All-Sky' data release,
as opposed to the superior ``AllWISE'' catalogs. That sample only
examined the 31 known $z>6$ quasars; our sample has 148 objects with
redshift $z\geq6.00$.

@@

This paper can be considered an update of \citet{Blain2013} and also
an extension of parts of \citet{Banados2016}, with the latter study reporting
WISE W1, W2, W3 and W4 magnitudes for Panoramic Survey Telescope and Rapid Response System 1 
\citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no  
further investigation into the reddest WISE waveband for the VH$z$Qs.
%%
\citet{Banados2016} reports and investigates the W1, W2 and W3 properties
of quasars at $z > 5.6$.

@@

Because of established conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4 magnitudes are calibrated on the Vega system (Wright et al. 2010). For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011, Brown2014b}. We make use of the Explanatory Supplement to the WISE All-Sky Data Release, as well as the WISE AllWISE Data Release  Products online. All optical ($ugriz$ bands) magnitudes are given in the AB system, all near-infrared  ($y/YJHK$) are also given in the AB system.  We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$,  $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016) in order to be consistent with \citet{Banados2016}.

@@

Table~\ref{tab:THE_TABLE} gives the salient details for the objects
used in this study. We use all the $z\geq5.00$ quasars that
have been discovered and spectroscopically confirmed as of the time of
writing (2018 June). We report near-infrared ($yYJHK$-bands)
and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
$M_{1450}$

@@

@@

Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
\citet{Jiang2008}, \citet{Wang2008} \citet{Jiang2009} \citet{Kurk2009}
\citet{Mortlock2009} \citet{Willott2009} \citet{Carilli2010}
\citet{Wang2010} \citet{Willott2010a} \citet{Willott2010b}
\citet{DeRosa2011} \citet{Mortlock2011} \citet{Wang2011}
\citet{Zeimann2011} \citet{Morganson2012} \citet{Venemans2012}
\citet{McGreer2013} \citet{Venemans2013} \citet{Wang2013}
\citet{Willott2013b} \citet{Banados2014} \citet{Calura2014}
\citet{Leipski2014} \citet{Banados2015a} \citet{Banados2015b}
\citet{Becker2015} \citet{Carnall2015} \citet{Jiang2015}
\citet{Kashikawa2015} \citet{Kim2015} \citet{Reed2015}
\citet{Venemans2015a} \citet{Venemans2015b} \citet{Willott2015}
\citet{Wu2015} \citet{Venemans2016} \citet{Wang2016_WISE}
\citet{Matsuoka2016} \citet{WangR2016} , \citet{Mortlock2011},
\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a}
and \citet{Matsuoka2018b}.

\subsection{Optical Photometry}
\subsubsection{Pan-STARRS1 (PS1)} 
We query the Panoramic Survey Telescope and Rapid Response System
(Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}}
Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs)
service at
\href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}.
The PS1 survey observed the 30,000 deg$^{2}$ of sky north of
declination $-30$ degrees in five filters $grizy$.  Pan-STARRS1 (PS1)
is the first part of Pan-STARRS to be completed and is the basis for
the DR1.  \citet{Chambers2016}, \citet{Magnier2016a},
\citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and
\citet{Flewelling2016} describe the instrument, survey, and data
analyses.  The principal science product of the PS1 survey is the
catalog accessible through the CasJobs interface.

We query and return the mean PSF magnitudes from the $grizy$ filters
({\tt MeanPSFMag}) which are in the AB system for our 425 VH$z$Q
sample. Details of our SQL and links to the main tables are given
in~\ref{sec:PS1_SQL}.

@@

\subsubsection{UKIDSS LAS} 
Use:\\
%lasDetection \\
dr10plus\\
lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
424 results returned. Of which...

\subsubsection{VISTA VHS} 
Use:\\
%lasDetection \\
VH5DR5 \\
sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
424 results returned.  Of which...

{\it N.B.}, a few objects will have both UKIDSS LAS and VISTA VHS photometry...

\iffalse
\subsection{Filter and Survey choices} 
We make some choices when reporting our archival photometry. 
This includes:
\begin{itemize}
\item Report Pan-STARRS1 DR1 $grizy$ wherever we have it; 
\item Report WFCAM $YJHK$ (mainly from the UKIDSS); 
\item Report VIRCAM $YJHK_{\rm S}$ (mainly from the VISTA surveys); 
\item Report VIRCAM $YJH$ over WFCAM  $YJH$; 
\item Report both VIRCAM $K_{\rm S}$ and WFCAM  $K$; 
\item Report DECam $grz$ wherever we have it (mainly from the DES and DECaLS); 
\item Due to lack of coverage, do not report WFCAM $Z$-band. 
\end{itemize}
\fi

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

    \subsection{Very High-$z$ Quasars Detected in WISE}
     \citet{Blain2013}

    \subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}

\subsection{Colours}

%%\subsection{Mullaney SEDs}

\subsection{Number Density of High-$z$ Sources}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}
\label{sec:conclusions}
In this study, we have, for the first time, ompiled the list of all
$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
objects, given their detection rates and SEDs. We find that::

@@

\section*{Acknowledgements}
NPR acknowledges support from the STFC and the Ernest Rutherford Fellowship scheme.

We thank Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface.

This paper heavily used \href{http://www.star.bris.ac.uk/~mbt/topcat/}{TOPCAT} (v4.4)
\citep[][]{Taylor2005, Taylor2011}.

This research made use of \href{http://www.astropy.org}{\tt Astropy}, 
a community-developed core Python package for Astronomy 
\citep{AstropyCollaboration2013, AstropyCollaboration2018}.

The Pan-STARRS1 Surveys (PS1) and the PS1 public science archive have
been made possible through contributions by the Institute for
Astronomy, the University of Hawaii, the Pan-STARRS Project Office,
the Max-Planck Society and its participating institutes, the Max
Planck Institute for Astronomy, Heidelberg and the Max Planck
Institute for Extraterrestrial Physics, Garching, The Johns Hopkins
University, Durham University, the University of Edinburgh, the
Queen's University Belfast, the Harvard-Smithsonian Center for
Astrophysics, the Las Cumbres Observatory Global Telescope Network
Incorporated, the National Central University of Taiwan, the Space
Telescope Science Institute, the National Aeronautics and Space
Administration under Grant No. NNX08AR22G issued through the Planetary
Science Division of the NASA Science Mission Directorate, the National
Science Foundation Grant No. AST-1238877, the University of Maryland,
Eotvos Lorand University (ELTE), the Los Alamos National Laboratory,
and the Gordon and Betty Moore Foundation.

CasJobs was originally developed by the Johns Hopkins University/
Sloan Digital Sky Survey (JHU/SDSS) team. With their permission, MAST
used version 3.5.16 to construct CasJobs-based tools for GALEX,
Kepler, the Hubble Source Catalog, and PanSTARRS.

This publication makes use of data products from the Wide-field
Infrared Survey Explorer, which is a joint project of the University
of California, Los Angeles, and the Jet Propulsion
Laboratory/California Institute of Technology, and NEOWISE, which is a
project of the Jet Propulsion Laboratory/California Institute of
Technology. WISE and NEOWISE are funded by the National Aeronautics
and Space Administration.

@@

\appendix

\section{PanSTARRS1 SQL queries}\label{sec:PS1_SQL}
The PS1 Casjobs SQL Server is located at
\href{http://mastweb.stsci.edu/ps1casjobs}{mastweb.stsci.edu/ps1casjobs}.
The top level documentation is given
\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs}{here}
while the description of tables is given
\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs#PS1Sourceextractionandcatalogs}{here}. The
main tables are the
\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+ObjectThin+table+fields}{{\tt
objectThin}} and
\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+MeanObject+table+fields}{{\tt
meanObject}} tables.

\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
Here we give the receipe and SQL that returned the near-infrared photometry 
for the VH$z$Qs.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Very high redshift quasars (VH$z$Qs; $z\gtrsim5$) are excellent probes
of the early Universe. This includes studies of the Epoch of
Reionization for hydrogen \citep[see e.g.][for reviews]{Fan2006review,
Mortlock2016}, the formation and build-up of supermassive black holes
\citep[e.g., ][]{Rees1984, WyitheLoeb2003, Volonteri2010, Agarwal2016,
Valiante2018, Latif2018} and early metal enrichment \citep[see e.g.,
][]{Simcoe2012, Chen2017, Bosman2017}.

There is a remarkable similarity between cosmic star-formation rate
density (SFRD) and black hole accretion rate (BHAR) trace each other
\citep[with a normalisation factor of $\sim3000$,][]{Willott2013b,
MadauDickinson2014} across redshifts $z=0-4$.  However, new results
\citet[e.g., ][]{Vito2018a, Calhau2018} suggest that the SFRD and BHAR
do not have the same evolutionary form at higher, $z>4$ redshifts, for
reasons that are currently poorly understood.
%% For some high-$z$ QSOs we can measure BHAR and SFR: most have BHAR $\gg 10^{-3}$ SFR.

@@

However, \citet{Blain2013} was compiled with the WISE `All-Sky' 
data release, as opposed to the superior ``AllWISE'' catalogs and 
only examined the 31 known $z>6$ quasars. Our sample has 
148 objects with redshift $z\geq6.00$.

@@

In this paper, we introduce the ``WISE W4 Compendium'' (WW4C); a
detailed study into the objects that were detected in the longest
waveband, 20-28$\mu$m observed, on the Wide-Field Infrared Survey
Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
%%
This study will describe all 40 million objects that are detected in
the WISE W4-band, but will concentrate on those objects most affected
by radiating dust emission and well described by extragalactic, and
AGN, spectral energy distributions (SEDs).  The motivations of the
WW4C are numerous, but the primary science we will pursue is the
identification of bolometric luminous AGN, especially those that might
not be observered in X-ray/UV/optical surveys.
%%
However, we will aim to remain as agnostic as possible to the origin
of the objects that are emit in the mid-infrared.

This paper can be considered an update of \citet{Blain2013} and also
an extension of \citet{Banados2014}, with the latter study reporting
WISE W1, W2, W3 and W4 magnitudes for Panoramic Survey Telescope and Rapid Response System 1 
\citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no  
further investigation into the reddest WISE waveband for the VH$z$Qs.
%%
\citet{Banados2016} reports and investigates the W1, W2 and W3 properties
of quasars at $z > 5.6$.

@@

Because of established conventions, we report SDSS $ugriz$ magnitudes on
the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, 
while the WISE W1 − 4 magnitudes are calibrated on the Vega system
(Wright et al. 2010). For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m =
(2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively
\citep{Cutri2011, Brown2014b}. We make use of the Explanatory Supplement to the
WISE All-Sky Data Release, as well as the WISE AllWISE Data Release
Products online.
All optical ($ugriz$ bands) magnitudes are given in the AB system, all near-infrared 
($y/YJHK$) are also given in the AB system. 
Our chosen cosmology is: 
%%
We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, 
$\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016).
in order to be consistent with \citet{Banados2016}.

@@

Table~\ref{tab:THE_TABLE} gives the salient details for the objects
used in this study. We use all the $z\geq5.00$ quasars that
have been discovered and spectroscopically confirmed as of the time of
writing (2018 June). We report near-infrared ($yYJHK$-bands)
and mid-infrared (WISE W1/2/3/4) photometry.

@@

\citet{Mortlock2011}, \citet{McGreer2013}, \citet{Venemans2013},  \citet{Venemans2013}, \citet{Venemans2015a},  \citet{Venemans2015b}, \citet{Banados2016}, \citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017}, \citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Matsuoka2017}, \citet{Tang2017}, \citet{Koptelova2017}, \citet{Matsuoka2017}, \citet{Banados2018}

@@

\citet{Fan2000}, \citet{Fan2001c}, \citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005}, \citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006}, \citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007}, \citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007}, \citet{Jiang2008}, \citet{Wang2008}         \citet{Jiang2009}         \citet{Kurk2009}          \citet{Mortlock2009}      \citet{Willott2009}       \citet{Carilli2010}       \citet{Wang2010}          \citet{Willott2010a}      \citet{Willott2010b}      \citet{DeRosa2011}        \citet{Mortlock2011}     \citet{Wang2011}          \citet{Zeimann2011}       \citet{Morganson2012}    \citet{Venemans2012}      \citet{McGreer2013}       \citet{Venemans2013}      \citet{Wang2013}         \citet{Willott2013b}     \citet{Banados2014}       \citet{Calura2014}        \citet{Leipski2014}       \citet{Banados2015a}      \citet{Banados2015b}      \citet{Becker2015}        \citet{Carnall2015}       \citet{Jiang2015}        \citet{Kashikawa2015}    \citet{Kim2015}          \citet{Reed2015}          \citet{Venemans2015a}    \citet{Venemans2015b}    \citet{Willott2015}      \citet{Wu2015}           \citet{Venemans2016}      \citet{Wang2016_WISE}    \citet{Matsuoka2016}      
\citet{WangR2016}

@@

\subsection{The WISE W4 Catalogue}
There are 747,634,026 total entries in the AllWISE Source Catalog.  Of
these, 40,939,966 (5.476\%) are W4-detected.

\begin{table}
  \begin{center}
    \begin{tabular}{l rr}
      \hline
      \hline
      Description & \#  objects & \% of Total \\         
      \hline  
      AllWISE Source Catalog & 747,634,026  & 100.0000 \\
      All W4 detections          &  40,939,966  &      5.4759 \\
      W4 Only                        &         35,818  &      0.0048\\
     \hline
      \hline
    \end{tabular}
    \caption{}
    \label{tab:ERQ_key_numbers}
  \end{center}
  \vspace{-8pt}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   5         S E C T I O  N   5           S E C T I O  N   5       S E C T I O  N   5
%%  S E C T I O  N   5         S E C T I O  N   5           S E C T I O  N   5       S E C T I O  N   5
%%  S E C T I O  N   5         S E C T I O  N   5           S E C T I O  N   5       S E C T I O  N   5
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Very High-$z$ Quasars Detected in WISE}
\citet{Blain2013} 
Cum sociis natoque penatibus et magnis dis parturient montes, nascetur
ridiculus mus. Mauris at diam quis arcu pretium dictum. Quisque id
risus odio. Pellentesque posuere semper tempor. Donec volutpat quam ut
urna rutrum venenatis dapibus nunc interdum. Sed quis diam ac mauris
cursus accumsan. Maecenas sit amet libero in elit mattis iaculis sed
quis elit. Pellentesque vitae mauris nunc.

\subsection{Very High-$z$ Quasars Detected in WISE W4}

\subsection{Colours}
Cras scelerisque egestas ante vitae lacinia. Nunc velit nunc, tempus
congue lobortis auctor, pellentesque ac ipsum. Donec erat urna,
interdum eget blandit non, malesuada nec tellus. Aliquam erat
volutpat. Maecenas ut eros id lorem suscipit vulputate pulvinar quis
libero. Phasellus ipsum libero, sollicitudin vel luctus in, faucibus
at mauris. Fusce ultrices egestas turpis, eget mattis tellus
pellentesque vel. Donec ut ligula id nisi commodo tristique. Etiam
semper turpis eget purus rhoncus a malesuada massa ultrices. Fusce
luctus vehicula sem, eget scelerisque lacus fermentum sed. Nulla
facilisi. Aenean ut turpis sed quam ullamcorper mattis sit amet ut
justo. Morbi lorem dui, aliquam et pharetra non, luctus eu enim. Nulla
molestie hendrerit mi tincidunt interdum. Nunc a augue nunc.

\subsection{Mullaney SEDs}

\subsection{Number Density of High-$z$ Sources}
Cras quis nisl eget orci ultricies tempor quis id mi. Nullam ut
sollicitudin justo. Maecenas posuere fermentum nunc et
faucibus. Integer consectetur nibh a dolor blandit ornare. In et dui
id sapien suscipit commodo eget vitae dolor. Cum sociis natoque
penatibus et magnis dis parturient montes, nascetur ridiculus
mus. Donec ut elit sed urna semper imperdiet nec ac lorem. Integer
varius nibh a mauris posuere non convallis nibh commodo. Cras posuere
lorem sit amet orci elementum sit amet dapibus risus lacinia. Morbi
vitae lobortis dui. Nulla ac lacus tellus, a volutpat tortor.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}
\label{sec:conclusions}
Cum sociis natoque penatibus et magnis dis parturient montes, nascetur
ridiculus mus. Duis tempus, lectus nec ultricies mollis, mi orci
feugiat nulla, a bibendum velit orci nec lacus. Duis a odio in nisi
egestas dictum. Nullam vel quam mauris, eget consectetur orci. Morbi
ac mi sit amet neque consectetur tempus ac eget est. Curabitur
malesuada arcu sit amet metus dictum at dapibus arcu accumsan. Fusce
sollicitudin luctus rutrum.

@@

\section*{Acknowledgements}

@@

\appendix
\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
Here we give the receipe and SQL that returned the near-infrared photometry 
for the VH$z$Qs.
